### 2018-03-29 latex/sc18/algorithm.tex
Changed algorithm1 and algorithm2 to use R instead of k to denoate the rank

\subsection{Dimension Trees}

@@

\subsection{Relative Error Computation}

@@

\subsubsection{Data Distribution}

@@

\begin{algorithm}
\caption{$\CP = \text{Par-NNCP}(\TA,k)$}
\label{alg:Par-NNCP-short}
\begin{algorithmic}[1]
\Require $\TA$ is an $I_1\times \cdots \times I_N$ tensor distributed across a $P_1\times \cdots \times P_N$ grid of $P$ processors, so that $\TA_{\V{p}}$ is $(I_1/P_1)\times \cdots \times (I_N/P_N)$ and is owned by processor $\V{p}=(p_1,\dots,p_N)$, $k$ is rank of approximation
\For{$n=2$ to $N$}
	\State Initialize $\Mn{H}{n}_{\V{p}}$ of dimensions $(I_n/P)\times k$ 
	\State $\M[\overline]{G} = \text{Local-SYRK}(\Mn{H}{n}_{\V{p}})$
	\State $\Mn{G}{n} = \text{All-Reduce}(\M[\overline]{G},\textsc{All-Procs})$
	\State $\Mn{H}{n}_{p_n} = \text{All-Gather}(\Mn{H}{n}_{\V{p}},\textsc{Proc-Slice}(n,\VE{p}{n}))$
\EndFor
\State \Comment{Compute NNCP approximation}
\While{not converged}
	\label{line:while}
	\State \Comment{Perform outer iteration of BCD}
	\For{$n=1$ to $N$}
		\label{line:for}
		\State \Comment{Compute new factor matrix in $n$th mode}
		\State $\M[\overline]{M} = \text{Local-MTTKRP}(\TA_{p_1\cdots p_N},\{\Mn{H}{i}_{p_i}\},n)$
			\label{line:locMTTKRP}
		\State $\Mn{M}{n}_{\V{p}} = \text{Reduce-Scatter}(\M[\overline]{M},\textsc{Proc-Slice}(n,\VE{p}{n}))$ 
			\label{line:reduce-scatter}
		\State $\Mn{S}{n} = \Mn{G}{1} \Hada \cdots \Hada \Mn{G}{n-1} \Hada \Mn{G}{n+1} \Hada \cdots \Hada \Mn{G}{N}$
			\label{line:hadamard}
		\State $\Mn{H}{n}_{\V{p}} = \text{Local-NLS-Update}(\Mn{S}{n},\Mn{M}{n}_{\V{p}})$
			\label{line:locNLS}
		\State \Comment{Organize data for later modes}
		\State $\M[\overline]{G} = {\Mn{H}{n}_{\V{p}}}^\Tra\Mn{H}{n}_{\V{p}}$
			\label{line:locSYRK}
		\State $\Mn{G}{n} = \text{All-Reduce}(\M[\overline]{G},\textsc{All-Procs})$
			\label{line:all-reduce}
		\State $\Mn{H}{n}_{p_n} = \text{All-Gather}(\Mn{H}{n}_{\V{p}},\textsc{Proc-Slice}(n,\VE{p}{n}))$
			\label{line:all-gather}
	\EndFor 
		\label{line:endfor}
\EndWhile
	\label{line:endwhile}
\Ensure $\TA \approx \CP$
\Ensure Local matrices: $\Mn{H}{n}_{\V{p}}$ is $(I_n/P)\times k$ and owned by processor $\V{p}=(p_1,\dots,p_N)$, for $1\leq n \leq N$, $\V{\lambda}$ stored redundantly on every processor
\end{algorithmic}
\end{algorithm}

>>>>

\subsection{Dimension Trees}
\label{sec:dimtrees}

@@

\subsection{Relative Error Computation}
\label{sec:error}

@@

\subsubsection{Data Distribution}
\label{sec:datadist}

@@

\begin{algorithm}
\caption{$\CP = \text{Par-NNCP}(\TA,R)$}
\label{alg:Par-NNCP-short}
\begin{algorithmic}[1]
\Require $\TA$ is an $I_1\times \cdots \times I_N$ tensor distributed across a $P_1\times \cdots \times P_N$ grid of $P$ processors, so that $\TA_{\V{p}}$ is $(I_1/P_1)\times \cdots \times (I_N/P_N)$ and is owned by processor $\V{p}=(p_1,\dots,p_N)$, $R$ is rank of approximation
\For{$n=2$ to $N$}
	\State Initialize $\Mn{H}{n}_{\V{p}}$ of dimensions $(I_n/P)\times R$ 
	\State $\M[\overline]{G} = \text{Local-SYRK}(\Mn{H}{n}_{\V{p}})$
	\State $\Mn{G}{n} = \text{All-Reduce}(\M[\overline]{G},\textsc{All-Procs})$
	\State $\Mn{H}{n}_{p_n} = \text{All-Gather}(\Mn{H}{n}_{\V{p}},\textsc{Proc-Slice}(n,\VE{p}{n}))$
\EndFor
\State \Comment{Compute NNCP approximation}
\While{not converged}
	\label{line:while}
	\State \Comment{Perform outer iteration of BCD}
	\For{$n=1$ to $N$}
		\label{line:for}
		\State \Comment{Compute new factor matrix in $n$th mode}
		\State $\M[\overline]{M} = \text{Local-MTTKRP}(\TA_{p_1\cdots p_N},\{\Mn{H}{i}_{p_i}\},n)$
			\label{line:locMTTKRP}
		\State $\Mn{M}{n}_{\V{p}} = \text{Reduce-Scatter}(\M[\overline]{M},\textsc{Proc-Slice}(n,\VE{p}{n}))$ 
			\label{line:reduce-scatter}
		\State $\Mn{S}{n} = \Mn{G}{1} \Hada \cdots \Hada \Mn{G}{n-1} \Hada \Mn{G}{n+1} \Hada \cdots \Hada \Mn{G}{N}$
			\label{line:hadamard}
		\State $\Mn{H}{n}_{\V{p}} = \text{Local-NLS-Update}(\Mn{S}{n},\Mn{M}{n}_{\V{p}})$
			\label{line:locNLS}
		\State \Comment{Organize data for later modes}
		\State $\M[\overline]{G} = {\Mn{H}{n}_{\V{p}}}^\Tra\Mn{H}{n}_{\V{p}}$
			\label{line:locSYRK}
		\State $\Mn{G}{n} = \text{All-Reduce}(\M[\overline]{G},\textsc{All-Procs})$
			\label{line:all-reduce}
		\State $\Mn{H}{n}_{p_n} = \text{All-Gather}(\Mn{H}{n}_{\V{p}},\textsc{Proc-Slice}(n,\VE{p}{n}))$
			\label{line:all-gather}
	\EndFor 
		\label{line:endfor}
\EndWhile
	\label{line:endwhile}
\Ensure $\TA \approx \CP$
\Ensure Local matrices: $\Mn{H}{n}_{\V{p}}$ is $(I_n/P)\times R$ and owned by processor $\V{p}=(p_1,\dots,p_N)$, for $1\leq n \leq N$, $\V{\lambda}$ stored redundantly on every processor
\end{algorithmic}
\end{algorithm}
